Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach

### 2021-09-17 Documents/Bookdown/index.Rmd
add first part bookdwon chpter descriptive stsatistics

--- 
title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Suppleemental Material of the article ..."
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

@@

                      # Code output width
                      tidy=TRUE, tidy.opts = list(width.cutoff = 80),
                      # comment = NA, prompt = TRUE

@@

## ggplot settings
theme_set(theme_classic()+
            theme(text = element_text(size=12)))

@@

drake_load_paper()
```

# Prerequisites {-}

trial

>>>>

--- 
title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Supplemental Material of the article “Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach”"
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

@@

                      # Code output width
                      tidy=TRUE, tidy.opts = list(width.cutoff = 80),
                      # comment = NA, prompt = TRUE,
                      collapse = TRUE,

@@

## ggplot settings
theme_set(theme_bw()+
            theme(text = element_text(size=12)))

@@

drake_load_bookdown()
```

# Introduction {-}

This is the Supplemental Material of the article “*Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach*” [TODO: add cit]. The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.

## Study Summary {-}

When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate. Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called “*informative hypotheses*”. However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses. An alternative approach is to use the Bayes Factor. In particular, the Bayes Factor based on the “*encompassing prior approach*” allows researchers to easily evaluate complex informative hypotheses. In this paper we provide a clear and detailed introduction to this approach. We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach. Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development.

## Supplemental Material Structure {-}

In the supplemental material we provide the complete statistical analyses of the case study regarding attachment. For more information regarding the Bayes Factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article]. The supplemental material is structure as follow:

- **Chapter \@ref(case-study) - Case Study.** We describe the sample included in the study and present the results of the cluster analysis to classify the different attachment patterns.
- **Chapter \@ref(ext) - Externalizing Problems.** The analyses regarding externalizing problems are presented. First, we conduct the analysis following the traditional NHST approach. Subsequently, we consider Bayesian Model Comparison using the WAIC and LOO as criteria. Finally, we consider the Bayes Factor with encompassing prior approach.
- **Chapter \@ref(int) - Internalizing Problems.** The analyses regarding internalizing problems are presented. The analyses follow the same structure as the case of externalizing problems. Thus, only differences will be highlighted.

## GitHub {-}

All the materials are available at the GitHub repository https://github.com/ClaudioZandonella/Attachment.

Refer to the `README` file for further information.
